\subsection{Virtual Private Network}
To allow the Acme Corp. sales department to access the web server 
externally, the upgraded network implementation includes a Virtual Private 
Network (VPN) server. The VPN server provides a secure and reliable private 
connection between computer networks over an existing public network. Once
connected to the Acme Corp. network securely through the VPN, Sales users are
able to access relevant network resources as if they were connected to a
physical interface on the Acme Corp. Premises.

\noindent
There are two components required in the remote-access VPN configuration:
\begin{enumerate}
    \item Network Access Server (NAS): a user can connect to the NAS from the
		Internet with valid credentials that are authenticated through the
        Active Directory server to sign in to the VPN.
	\item Client Software: in order to establish and maintain a connection
		to the VPN. The client software sets up the tunneled connection to the 
        NAS that can connect from any public network from the Internet. 
\end{enumerate}

\noindent
Acme Corp.'s VPN server uses OpenVPN to create the VPN.
\subsubsection{Network/Interface Information}
\textbf{Network Gateway} \\
The VPN server itself connects to the network through Fa0/3 of Switch 7 and is 
a member of the Acme Corp. "Demilitarized Zone". The default gateway for the VPN 
server is the static IP for Fa0/3 on the \textbf{10.1.10.0/24} subnet, TBD. \\

\noindent
\textbf{IP Address} \\
The VPN server is a member of the External Services ("DMZ"), and is
likewise configured on subnet \textbf{10.1.170.x}, with a static IP address of 
\textbf{10.1.170.3}. \\

\subsubsection{Server Setup/Configuration}
OpenVPN is installed on the VPN server and authenticates users with Active
Directory.

\subsubsection{Client Setup/Configuration}
OpenVPN may be used as a VPN client to connect to the Acme Corp. VPN server, 
but any VPN bundled with an operating system may work as well. \\

\subsubsection{VPN Connection Information}
The Acme Corp. VPN can be reached from the Internet at the address:

\begin{lstlisting}[backgroundcolor=\color{Gray}]
 vpn.acme.com
\end{lstlisting}
*login and password are the same login and password configured in Active
Directory.
