\subsection{Web server}
The Acme Corp. web server must host a website that is accessible to Sales, and a 
back-end database that is accessible to HR. \\

\noindent
\textbf{Assumption!}: The network upgrade requirements do not state what Sales 
will be using the website for (i.e. Retrieving information only or also
creating/updating information). At the time of the upgrade, it is assumed that
the website is solely a tool that Sales uses to show-off Acme Corp's products 
to potential clients. If the requirements of the network change in the future 
and Sales requires CRUD functionality, it is trivial to create a new database 
and setup appropriate accounts and permissions to allow such functionality.

\subsubsection{Network/Interface Information}
\textbf{Network Gateway} \\
The web server connects to the network through Fa0/1 of Switch 7 and is a 
member of the Acme Corp. "Demilitarized Zone". The default gateway for the web 
server is the static IP for Fa0/1 on the \textbf{10.1.10.0/24} subnet, TBD. \\

\noindent
\textbf{IP Address} \\
The web server is a member of the External Services (DMZ), and is likewise
configured on the subnet 10.1.170.x, with a static IP address of
\textbf{10.1.160.1}.

\subsubsection{Server Setup/Configuration}
The Acme Corp. web server will run a LAMP stack using Apache and PHP. The
following will install the necessary packages on the web server (the database 
is installed on a separate server, so it is not a required package on the web
server). \\

\begin{lstlisting}[language=bash, backgroundcolor=\color{Gray}, 
escapeinside={(*}{*)}]
 (*\#*) apt install apache2 php7.0 libapache2-mod-php7.0 \
        php7.0-mcrypt php7.0-mysql
\end{lstlisting}
\vspace{1em}

\noindent
Additionally, a few default files should be edited as demonstrated below. \\

\begin{lstlisting}
 /etc/apache2/sites-enabled/000-default.conf
\end{lstlisting}
\vspace{1em}

\noindent
ServerAdmin directive should be changed to "systems@acme.com". \\

\begin{lstlisting}
 /etc/apache2/apache2.conf
\end{lstlisting}
\vspace{1em}

\noindent
Remove \lstinline$FollowSymLinks$ from the \lstinline$<Directory /var/www/>$
scope. \\

\noindent
Additionally, the following should be appended to the end of the file: \\

\begin{lstlisting}[language=bash, backgroundcolor=\color{Gray}]
ServerName 'web.acme.com' 
\end{lstlisting}
\vspace{1em}
