\subsection{Dynamic Host Configuration Protocol}
The Dynamic Host Configuration Protocol (DHCP) for Acme Corp. uses the 
\lstinline$isc-dhcp-server$ package. \\

\noindent
The DHCP server serves requests for IP addresses for the user hosts 
(workstations). Other hosts, such as members of the Internal/External zones,
switches, and routers are manually configured with a static IP.

\subsubsection{Network/Interface Information}
\textbf{Network Gateway} \\
The DHCP server itself connects to the network through Fa0/1 of Switch 6 and is 
a member of the Acme Corp. "Server Zone". The default gateway for the DHCP 
server is the static IP for Fa0/1 on the \textbf{10.1.10.0/24} subnet, TBD. \\

\noindent
\textbf{IP Address} \\
The DHCP server is a member of the Internal Services ("Server Zone"), and is
likewise configured on subnet \textbf{10.1.160.x}, with a static IP address of 
\textbf{10.1.160.1}. \\

\subsubsection{Server Setup/Configuration}
To configure the DHCP server, the \lstinline$isc-dhcp-server$ package must be 
installed on the host that will act as the DHCP server. \\

\begin{lstlisting}[language=bash, backgroundcolor=\color{Gray}, 
escapeinside={(*}{*)}]
 (*\#*) apt install isc-dhcp-server
\end{lstlisting}
\vspace{1em}

\noindent
Additionally, some config files must be modified from the defaults. \\

\begin{lstlisting}
 /etc/dhcp/dhcpd.conf
\end{lstlisting}
\vspace{1em}

\noindent
The following changes should be made:
\begin{lstlisting}[backgroundcolor=\color{Gray}]
 option domain-name "acme.com";
 option domain-name-servers 10.1.160.2;
 subnet 10.1.110.0 netmask 255.255.255.0 {
     default-lease-time 259200;
     max-lease-time 259200;
     pool {
         range 10.1.110.1 10.1.110.254;

     }

 }
 subnet 10.1.120.0 netmask 255.255.255.0 {
     default-lease-time 259200;
     max-lease-time 259200;
     pool {
         range 10.1.120.1 10.1.120.254;

     }

 }
 subnet 10.1.130.0 netmask 255.255.255.0 {
     default-lease-time 259200;
     max-lease-time 259200;
     pool {
         range 10.1.130.1 10.1.130.254;

     }

 }
 subnet 10.1.140.0 netmask 255.255.255.0 {
     default-lease-time 259200;
     max-lease-time 259200;
     pool {
         range 10.1.140.1 10.1.140.254;

     }

 }
 subnet 10.1.150.0 netmask 255.255.255.0 {
     default-lease-time 259200;
     max-lease-time 259200;
     pool {
         range 10.1.150.1 10.1.150.254;

     }

 }
\end{lstlisting}

\subsubsection{Client Setup/Configuration}
User hosts (workstations) must be manually configured to connect to the network
through the static IP address of the respective Gateway (switch port) they are
connected to. This ensures the workstation can connect to the network and
request an IP address from the DHCP server.
